---
title: "Final Project"
author: "Vanessa Tang"
date: "4/19/2021"
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

---
title: "Network Measures"
author: "Vanessa Tang"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```

```{r}
library(igraph)
library(ggplot2)
# Load the data for econ sem1 to sem2 
sem_edge1=read.csv(file="/Users/vanessatang/registrar-recommender/03_intermediate/Mobility Matrix/semester1to2_econ_node.csv")
sem_edge1 = sem_edge1[,-1]
sem_attr1 = read.csv(file="/Users/vanessatang/registrar-recommender/03_intermediate/Mobility Matrix/semester1to2_econ_attr.csv")
sem_attr1 = sem_attr1[,-1]
class_netbyedgelist=graph_from_data_frame(d=sem_edge1, directed=T,vertices=sem_attr1)
indeg_igraph=degree(graph=class_netbyedgelist, mode="in")
centrality=centr_degree(graph=class_netbyedgelist, mode="in", 
                         loops=FALSE, normalized=TRUE)
centrality
```

## Lab 9

```{r}
# Loading data, setting up df

setwd("/Users/vanessatang/registrar-recommender/03_intermediate/Mobility Matrix")

edge1=read.csv(file="class1to2_econ_node.csv")
edge1 = edge1[,-1]
head(edge1) 

edge2=read.csv(file="class2to3_econ_node.csv")
edge2 = edge2[,-1]
head(edge1) 

sem_edge1=read.csv(file="semester1to2_econ_node.csv")
sem_edge1 = sem_edge1[,-1]

sem_edge_di1=read.csv(file="semester1to2_econ_node_di.csv")
sem_edge_di1 = sem_edge_di1[,-1]


attr1=read.csv(file="class1to2_econ_attr.csv")
attr2=read.csv(file="class2to3_econ_attr.csv")
sem_attr1 = read.csv(file="semester1to2_econ_attr.csv")
sem_attr1 = sem_attr1[,-1]

attr1 = attr1[,-1]
attr2 = attr2[,-1]

head(attr1) 
```

```{r}
library(igraph)

# Create graphs from edge df
edge_graph=graph_from_data_frame(d=edge1, directed=T,
                                    vertices=attr1) 
edge_graph 

edge_graph2=graph_from_data_frame(d=edge2, directed=T,
                                 vertices=attr2) 

edge_graph_sem=graph_from_data_frame(d=sem_edge1, directed=T,
                                 vertices=sem_attr1) 
edge_graph_sem=graph_from_data_frame(d=sem_edge_di1, directed=T,
                                     vertices=sem_attr1)
```


## Centrality

```{r}
g = edge_graph_sem

class_netbyedgelist=graph_from_data_frame(d=sem_edge1, directed=T, vertices=sem_attr1)
centr_degree(graph=class_netbyedgelist, mode="in", loops=FALSE, normalized=TRUE)
```

Indegree
```{r}
indeg=degree(graph=g, mode="in")
data.frame(indeg)
```

Outdegree
```{r}
outdeg=degree(graph=g, mode="out")
data.frame(outdeg)
```

Out closeness: mean distance of each node to all other nodes
```{r}
out_closeness=closeness(graph=g, mode="out", normalized=F)
data.frame(out_closeness)
```

In closness
```{r}
in_closeness=closeness(graph=g, mode="in", normalized=F)
data.frame(in_closeness)
```

Can use distance matrix to solve problem of infinite distances (isolates)
```{r}
dist_mat_social=distances(graph=g, mode="out") #calculating the 
#distance matrix
diag(dist_mat_social)=NA #ignoring the diagonal
dist_mat_social_inverted=1/dist_mat_social #getting inverted distance matrix

out_closeness2=apply(dist_mat_social_inverted, MARGIN=1, 
                           FUN=mean, na.rm=T) 
data.frame(out_closeness2)
```

Comparing different ways of calculating out closeness (function vs distance matrix)
```{r}
cor(out_closeness, out_closeness2) 
```

Another way to compute in closness using distance matrix
```{r}
in_closeness2=apply(dist_mat_social_inverted, MARGIN=2,
                          FUN=mean, na.rm=T) 
data.frame(in_closeness2)
```

Betweenness centrality: num of shortest paths going through vertex
```{r}
betweenness_social=betweenness(graph=g, normalized=F) 
data.frame(betweenness_social)
```

Eigenvector centrality: greater weight to node when more connected to other highly connected nodes
- measuring node network importance
```{r}
g_undirected=as.undirected(g, mode="collapse") 

# eigenvector centrality
ev_obj_social=eigen_centrality(g_undirected)
eigen_cent=ev_obj_social$vector

data.frame(eigen_cent)
```

```{r}
ids=V(g)$name

central_social=data.frame(ids=ids, net="social",
                            indegree=indeg,
                            outdegree=outdeg,
                            incloseness=in_closeness, 
                            incloseness2=in_closeness2, 
                            outcloseness2=out_closeness2,
                            between=betweenness_social, 
                            eigen=eigen_cent)

apply(central_social[, -c(1,2)], MARGIN=2, FUN=order, decreasing=T)
```

```{r}
library(reshape)

social_long=melt(central_social[,c("ids", "indegree", "incloseness2",
                                   "between", "eigen")], id.vars="ids")  
head(social_long)

library(ggplot2)
ggplot(social_long, aes(x=factor(ids, levels=1:length(ids)), y=value))+
  geom_bar(stat="identity", position="dodge")+
  facet_wrap(~variable, scales="free_y", ncol=2)+
  xlab("Ids")+ylab("Centrality")+
 theme(axis.text=element_text(size=6.5))
```

```{r}
plot(g, vertex.size=central_social$between/5, 
     vertex.label=V(s641_social)$name, 
     edge.arrow.size=0.25,
     layout=layout.fruchterman.reingold, 
     main="Title", margin=0) 
```

### 2.2. Correlations between Centrality Measures

```{r}
cor_tab1=cor(central_social[,-c(1,2)])
round(cor_tab1[,c("indegree", "outdegree", "incloseness2", 
                            "outcloseness2", "between", "eigen")], 3)
```
